---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
devtools::install_github("mtoto/ufc.stats")
```
# ufc.stats

This package contains UFC fight statistics, continously updated with data from latest events. 

## Installation 

You can install the development version from [GitHub](https://github.com/) with:

``` {r}
# devtools::install_github("mtoto/ufc.stats")
data("ufc_stats")
```

Each row of `ufc_stats` represents the statistics of one fighter in a single round of a fight. The `data.frame` contains 37 variables in total. For full a description of each variable, please refer to the [Data Dictionary](http://tamaszilagyi.com/ufc.stats/docs/articles/data-dictionary.html) on the package's website.

## Example usage

Who has the most significant strikes landed in UFC history?

```{r dplyr, message=FALSE}
library(dplyr)

ufc_stats %>% group_by(fighter) %>%
  summarise(total_significant_strikes = sum(significant_strikes_landed)) %>%
  arrange(-total_significant_strikes) %>%
  head()
```

